Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-06-12 ms/Thesis/thesis.tex
Add paragraph in the intro about 'Human large-scale cooperation as a product of competition between cultural groups'

>>>>

\citet{handley2020human} showed the importance of culture on the human behavior. They showed that the probablity of indvidual to cooperate with unrelated strangers from a different group in transient interactions corresponds to the degree of cultural similarity between those groups.
Therefore, they have suggested that group-level selection on culturally differentiated populations can explain cooperation between unrelated humans from different groups.
